---
title: "Bellabeat - Google Data Analytics Case Study"
subtitle: "How Can a Wellness Technology Company Play It Smart?"
author: "Isabel Lebron"
date: "12/20/2021"
output: html_document
---

## Introduction to Bellabeat:
Bellabeat is a high-tech manufacturer of health-focused products for women. Founders, Urška Sršen and Sando Mur, developed technology for women to track their activity, sleep, stress, as well as reproductive health, and designed this technology in a new and beautiful way. With the goal to inspire women around the world, and empower them with knowledge regarding their own health and habits, Bellabeat created a product line including a variety of wellness products. These smart wellness products include a Bellabeat Leaf wellness tracker, a smartwatch, and a smart water bottle, all of which connect to the Bellabeat app, which provides access to the user’s health data.  

## Scenario:
With Bellabeat growing rapidly since its debut in 2013, they have the potential to grow even further and become a larger part of the global smart device market. With that being said, Urška Sršen, the cofounder and Chief Creative Officer of Bellabeat believes that analyzing smart device fitness data from other fitness-related devices, like FitBit, could help foster new growth opportunities and ideas for the company. I have been asked to focus on one of Bellabeat’s products and analyze smart device data to gain insight into how consumers are using their smart devices, which I will then use to help guide a new and improved marketing strategy for the company.

### Step 1: Ask
#### Business Task:
As an aspiring junior data analyst, I have been tasked with providing primary and secondary stakeholders with insightful recommendations for one of Bellabeat’s wellness products. I will be analyzing smart device user data in order to gain insight into how consumers are using their non-Bellabeat smart devices, and then apply these insights to comparable Bellabeat products such as the Bellabeat Time. \ 

#### Key Stakeholders:
**Primary stakeholders:**\

*  **Urška Sršen:** Bellabeat’s co-founder and Chief Creative Officer. \
*  **Sando Mur:** Mathematician and Bellabeat’s co-founder; a key member of the Bellabeat executive team.\

**Secondary Stakeholders:**\

*  **Bellabeat marketing analytics team:** The team I am "a part of" which includes data analysts responsible for collecting, analyzing, and reporting data that helps guide Bellabeat’s marketing strategy. \

#### Questions for the analysis:
1. What are some trends in smart device usage?
2. How could these trends apply to Bellabeat customers?
3. How could these trends help influence Bellabeat marketing strategy?\

### Step 2: Prepare
#### About the data:
The dataset for this case study, FitBit Fitness Tracker Data, comes from Kaggle and contains 18 .csv datasets in both long and wide formats. Each dataset consists of in-depth metrics regarding users’ heart rate, sleep monitoring, calories burned, and many more. The datasets were generated by respondents to a survey via Amazon Mechanical Turk, distributed between April 12th, 2016, and May 12th, 2016. Thirty eligible Fitbit users consented to the submission of personal tracker data, including minute-level output for physical activity, heart rate, and sleep monitoring.  

My analysis will be focusing on one product from Bellabeat’s product line, Bellabeat Time. In addition to telling time, this product tracks its users’ activity and sleep patterns and connects that information to the Bellabeat app, which then shares insights with its owner. For my analysis, I will be focusing on the following datasets:\

* dailyActivity_merged.csv, renamed DailyActivity.csv\
* sleepDay_merged.csv, renamed SleepDay.csv\
* weightLogInfo_merged.csv, renamed WeightLog.csv\

#### Limitations of the data

* It is very likely that the 33 survey participants aren’t an actual representation off all FitBit users. 
* The data is old, from 2016, and it is possible trends of using wearable smart fitness devices have changed. Additionally, it is likely both FitBit and Bellabeat have released smart devices since 2016. \

#### Data import / exploration
For my analysis, I will be using R Studio because of the many packages and data visualization features available to clean and analyze the data. \

##### Loading packages
```{r echo=T, message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(janitor)
library(dplyr)
library(lubridate)
library(ggplot2)
library(forcats)
```
\

##### Importing CSV files
Below we will be creating the data frames to be used for analysis. First, we will make sure to set our working directory to where our CSV files are located, then use the read_csv() function to import them. We will also be following typical naming conventions based on the names of the CSV files.
```{r echo=T, message=FALSE, warning=FALSE, results='hide'}
DailyActivity <- read_csv("DailyActivity.csv")
SleepDay <- read_csv("SleepDay.csv")
WeightLog <- read_csv("WeightLog.csv")
```
\

#### Exploring our data
Below we will take a sneak peek at our data frames by using the str() and colnames() functions. The head() function is used to get the first few rows in the data frame, while colnames() retrieves the column names in the data frame.

##### Daily Activity dataset
```{r}
head(DailyActivity)
colnames(DailyActivity)
```

##### Sleep dataset
```{r}
head(SleepDay)
colnames(SleepDay)
```

##### Weight Log dataset
```{r}
head(WeightLog)
colnames(WeightLog)
```

### Step 3: Process
During this phase, we will be cleaning our data by removing any duplicates or missing values from each dataset. Additionally, we will transform data into the right type if it is incorrectly formatted. 

#### Cleaning up:
##### Let's start with the DailyActivity dataset
```{r}
# Are there duplicates?
sum(duplicated(DailyActivity))
# Are there nulls?
sum(is.na(DailyActivity))
# Change name from ActivityDate to Date
names(DailyActivity)[names(DailyActivity) == "ActivityDate"] <- "Date"
# Change character format to date type
DailyActivity$Date <- as.Date(DailyActivity$Date, format = '%m/%d/%Y')
# Add day of the week column
DailyActivity$DayOfWeek <- wday(DailyActivity$Date, label = TRUE)
# Add total active minutes column
DailyActivity2 <- DailyActivity %>% 
  mutate(TotalActiveMinutes = VeryActiveMinutes + FairlyActiveMinutes + LightlyActiveMinutes)
# Check dataset
head(DailyActivity2)
colnames(DailyActivity2)
```
\

##### Next, let's clean the SleepDay dataset
```{r}
# Are there duplicates?
sum(duplicated(SleepDay))
# Remove duplicates
SleepDay2<-distinct(SleepDay)
# Make sure duplicates were removed
sum(duplicated(SleepDay2))
# Are there nulls?
sum(is.na(SleepDay2))
# Change name from SleepDay to Date
names(SleepDay2)[names(SleepDay2) == "SleepDay"] <- "Date"
# Change character format to date type
SleepDay2$Date <- as.Date(SleepDay2$Date, format = '%m/%d/%Y')
# Add day of the week column
SleepDay2$DayOfWeek <- wday(SleepDay2$Date, label = TRUE)
# Check dataset
head(SleepDay2)
colnames(SleepDay2)
```
\

##### Next, let's clean the WeightLog dataset
```{r}
# Are there duplicates?
sum(duplicated(WeightLog))
# Are there nulls?
sum(is.na(WeightLog$WeightPounds))
# Separate date and time
WeightLog2 <- WeightLog %>% 
  separate(Date, into=c("Date","Time"), sep=" ",remove =FALSE )
# Change character format to date type
WeightLog2$Date <- as.Date(WeightLog2$Date, format = '%m/%d/%Y')
# Add day of the week column
WeightLog2$DayOfWeek <- wday(WeightLog2$Date, label = TRUE)
# Check dataset
head(WeightLog2)
colnames(WeightLog2)
```
\

Now that we have removed any duplicates and missing values in the data, and correctly formatted the necessary data types, we can combine our three data frames into one big data frame and then move on to analyzing our data. \
\

##### Finally, merging our data
```{r}
Final <- merge(merge(DailyActivity2, SleepDay2, by = c('Id', 'Date'), all = TRUE), WeightLog2, by = c('Id', 'Date'), all = TRUE)
head(Final)
```
\

### Step 4: Analyze 
##### Let's first take a look at the number of participants in each dataset
```{r}
n_distinct(DailyActivity$Id)
n_distinct(SleepDay$Id)
n_distinct(WeightLog$Id)
```
Using the n_distinct() function we are able to determine the number of unique values in the 3 datasets. Compared to the daily activity and asleep data frames, the weight log data frame consists of a very low number of participants. We will explore this more later on. \
\

##### Now let's look at important statistics for each dataset
Using the summary() function, we are able to pull these important statistics for each of the datasets. \
\

**Merged data frame**
```{r}
Final %>% 
  select(TotalSteps, Calories,TotalActiveMinutes,TotalMinutesAsleep, BMI, IsManualReport ) %>% 
summary(Final)
```
**Notes**: Taking a look at some of these statistics we can gain some insight about the FitBit users. According to NBC "The fitness goal of 10,000 steps a day is widely promoted, but a new study suggests that logging even 7,000 daily steps may go a long way toward better health." From our summary statistics, we can see that on average, FitBit users were reaching 7,638 steps a day, which seems like a good amount according to NBC. We can take a look at more of these summary statistics below. \
\

**DailyActivity data frame**
```{r}
DailyActivity2 %>% 
  select(TotalSteps, TotalDistance, LightlyActiveMinutes, FairlyActiveMinutes, VeryActiveMinutes, SedentaryMinutes, Calories) %>% 
  summary()
```
**Notes:** As previously stated, the average amount of steps per day for FitBit users is 7,638. While the 10,000 steps per day number have been widely promoted over the years, studies from the National Institute of Health have found that some people may benefit from starting with goals of fewer than the common standard of 10,000 steps a day. In fact, death rates declined with more steps taken each day until about 7,500 steps a day, when the benefit leveled off. Therefore, with the average steps per day being 7,638 for FitBit users, it seems as though they are on the right track! So it is important not to discourage users if they are taking less than 10,000 steps per day. Additionally, FitBit users are averaging 991.2 minutes of sedentary time a day, this is roughly 16.5 hours a day! A new study suggests about 30-40 minutes per day of building up a sweat should help to counteract the negative health impact of sitting all day long. However, the 30-40 minutes is in regards to sitting at a desk for 10 hours, and on average the FitBit user’s sedentary time was 16.5 hours, so it is likely more than 40 minutes of working up a sweat is going to be needed to counteract that time sitting.\
\

**SleepDay data frame**
```{r}
SleepDay2 %>% 
  select(TotalSleepRecords,TotalMinutesAsleep,TotalTimeInBed) %>% 
  summary()
```
**Notes:** Taking a look at the summary of the sleep data frame, we can see that on average, a FitBit user sleeps for 419.2 minutes which is roughly 7 hours. This amount falls within the recommendations from the CDC for how much sleep adults should get. However, taking a look at the mean for total time in bed, we can see on average FitBit users spend 458.5 minutes in bed. This means that on average, participants are spending 39.3 minutes awake in bed. According to an article from Health Central, individuals should not spend any more than an hour awake in bed. By avoiding this, you are helping to prevent a mental link being formed between being in bed and being awake, which can essentially lead to insomnia or other sleep issues. \
\

**WeightLog data frame**
```{r}
WeightLog2 %>% 
  select(WeightPounds, BMI, IsManualReport) %>% 
  summary()
```
**Notes:** Taking a look at the summary statistics from the weight log dataset, the average BMI is 25.19. According to the CDC, a BMI above 25 is considered overweight, however, with very few participants logging their weight, we are unable to make any conclusions regarding BMI. With that being said, taking a look at the "IsManualReport" statistics, there are twice the amount of manually reported entries in the WeightLog table as non-manual entries. It could be beneficial to discover how dedicated FitBit users are when it comes to logging their weight, so we will dive deeper into this a little later. \
\

#### Analysis questions and answers:

##### Daily Activity
**1. What are some trends in smart device usage?**\
Taking a look at daily activity data, we can see that, on average, FitBit users are reaching 7,638 steps a day. We can also see that, on average, participants spend 227.5 minutes each day being active. These total active minutes include a sum of the amount of time the user spends participating in each level of activity: lightly active, moderately active, and very active. On the other hand, FitBit users are also averaging 991.2 minutes of sedentary time a day, which is roughly 16.5 hours! \

**2. How could these trends apply to Bellabeat customers?**\
I believe these trends could help make sure Bellabeat users get enough active time each day to counteract all the time they have spent sedentary.   \

**3. How could these trends help influence Bellabeat marketing strategy?**\
As previously discussed, although 10,000 steps a day has been widely promoted over the years by many fitness companies, studies show that even 7,500 daily steps could lead towards better health. Focussing on not discouraging Bellabeat’s customers, and potentially scaring them with big numbers, Bellabeat can help make users feel more comfortable and notify users throughout the day to get up and walk around and help them reach their goals. In addition to that, with the amount of time users spend sitting, I believe it could be beneficial for Bellabeat to recognize when a user has been sedentary for a while and encourage them to get up, even if it is for just a few minutes! \
\

##### Sleep
**1. What are some trends in smart device usage?**\
In this particular study, we have sleep data for 24 of the 33 participants, meaning roughly 73 percent of the users wore their smart devices to sleep. In addition, from the data, we can see that, on average, the majority of the users got the CDC-recommended 7 hours of sleep. In addition to hours asleep, taking a look at the time spent in bed versus the time users were asleep, we see that participants are seen spending, on average, 39.3 minutes awake in bed. \

**2. How could these trends apply to Bellabeat customers?**\
I believe these trends could help Bellabeat make sure their users are getting the necessary amount of sleep, as well as helping to avoid spending too much time in bed awake.  \

**3. How could these trends help influence Bellabeat marketing strategy?**\
While this is a relatively small study, and likely doesn't accurately represent the whole population of FitBit users, I think it is a safe assumption to say not all users wear their device to sleep, most likely due to comfortability. Bellabeat can focus on making their smart devices not only comfortable to wear day-to-day, but also comfortable to wear while asleep, and marketing that to potential customers. \
\

##### Weight Log
**1. What are some trends in smart device usage?**\
When it comes to smart device usage and users logging their weight, it seems like this area needs some improvements. Just looking at overall participants in the study, 8 of them used the weight log feature, that is only 24 percent! Additionally, of those 8 participants, 5 of them manually reported their weights, and 3 had their weight automatically reported using a smart scale.  \

**2. How could these trends apply to Bellabeat customers?**\
I believe these trends show that Bellabeat customers should feel comfortable reporting their weights and feeling empowered in doing so. Creating a body-positive environment for Bellabeat customers is extremely important!  \

**3. How could these trends help influence Bellabeat marketing strategy?**\
As previously mentioned, creating a body-positive environment for Bellabeat users could aid in the lack of users logging their weight. Creating this environment in advertisements, on the website, and within the app, can help with empowering our users to learn more about their health. In addition, I believe using smart scales could be a great way to help with the task of users manually reporting their weight. Marketing smart scales and incorporating easy connectivity to the app could lead to great success in increasing the number of users logging their weight! \

### Step 5: Share
I used the ggplot() function in order to create data visualizations that show patterns and trends that I found to be important in the data frames.\
\

#### Activity Visuals
**Let's take a look at the relationship between the different types of active minutes and total steps versus calories burned.**
```{r message=FALSE, warning=FALSE, figures-side, fig.show="hold", out.width="50%"}
# Relationship between very active minutes and calories burned
ggplot(data = DailyActivity2, aes(x=VeryActiveMinutes, y=Calories, color = Calories)) + 
  geom_point() +
  stat_smooth(method = lm) +
  labs(title = 'Very Active Minutes vs. Calories Burned', 
       x = "Very Active Minutes",y = "Calories Burned" )

# Relationship between fairly active minutes and calories burned
ggplot(data = DailyActivity2, aes(x=FairlyActiveMinutes, y=Calories, color = Calories)) + 
  geom_point() +
  stat_smooth(method = lm) +
  labs(title = 'Fairly Active Minutes vs. Calories Burned', 
       x = "Fairly Active Minutes",y = "Calories Burned" ) 

# Relationship between lightly active minutes and calories burned
ggplot(data = DailyActivity2, aes(x=LightlyActiveMinutes, y=Calories, color = Calories)) + 
  geom_point() +
  stat_smooth(method = lm) +
  labs(title = 'Lightly Active Minutes vs. Calories Burned', 
       x = "Lightly Active Minutes",y = "Calories Burned" )

# Relationship between total steps and calories burned
ggplot(data = DailyActivity2, aes(x=TotalSteps, y=Calories, color = Calories)) + 
  geom_point() +
  stat_smooth(method = lm) +
  labs(title = 'CTotal Steps vs. Calories Burned', 
       x = "Total Steps", y = "Calories Burned")
```
\
**Notes:** From the visuals above, we can see that the strongest positive relationship occurs between very active minutes and total daily calories burned. While this may be expected, it is still important to see if our data is being accurately represented. Taking a look at the relationship between fairly active minutes and calories burned, you can still see a positive relationship, however, it is not as strong as the first. With fairly active physical activity the participant still can burn a good amount of calories. In addition, the relationship between lightly active minutes and calories burned is significantly less positive than very active and fairly active when it comes to calories burned. This goes to show that the more vigorous physical activity the participant did, the more calories they burned. So if the goal is to lose weight and burn calories, it is important to incorporate more vigorous physical activity into one's day. 

Finally, taking a look at the relationship between total steps and calories burned, we see a relationship that one could expect. We clearly see a positive correlation depicting the more steps taken, the more calories are burned. So whether or not the goal is to lose weight, increasing the amount of steps taken each day can help to stay active and burn some calories!\
\

#### Sleep Visuals
**First, I plotted the relationship between total minutes asleep and total time in bed**
```{r}
ggplot(data = SleepDay2, aes(x = TotalMinutesAsleep, y = TotalTimeInBed)) +
  geom_point() +
  stat_smooth(method = lm) +
  labs(title = "Total Minutes Asleep vs. Total Time In Bed")
```
\
**Notes:** In the above visual, a positive relationship between total minutes asleep and total time in bed is seen. For the most part, the time users spent asleep and the time they spent in bed was very similar. This means that users are not spending too much time awake in bed which is important for their sleep health.\
\

**Next, I am going to plot the sleep distribution of the FitBit users to see whether or not they get enough sleep according to CDC standards.**
```{r}
SleepDay2 %>% 
  select(TotalMinutesAsleep) %>% 
  mutate(HoursAsleep = ifelse(TotalMinutesAsleep <= 420, 'Less than 7h',
                      ifelse(TotalMinutesAsleep <= 540, '7h to 9h',
                             'More than 9h'))) %>% 
  mutate(HoursAsleep = factor(HoursAsleep,
                              levels = c('Less than 7h', '7h to 9h','More than 9h'))) %>% 
  ggplot(aes(x = TotalMinutesAsleep, fill = HoursAsleep)) +
  geom_histogram(position = 'dodge', bins = 25) +
  theme_gray() +
   labs(title = "Sleep distribution",
       x = "Time asleep (minutes)",
       y = "Count")
```
\
**Notes:** To get an idea about FitBit's users’ sleep patterns, I decided to plot their sleep distribution to see if whether or not they get enough sleep according to CDC guidelines. By taking a look at the visual, we can see that participants follow healthy sleep patterns, getting between 6-9 hours of sleep per day, which is up to CDC's standards for getting enough rest.\
\

#### Weight Log Visuals
**Plotting Auto vs Manual reports of the weight data**
```{r}
ReportType <- c("Manual Report", "Auto Report")
ReportTypeTF <- c(length(which(WeightLog2$IsManualReport == "TRUE")), length(which(WeightLog2$IsManualReport == "FALSE")))
ReportDF <- data.frame(ReportType, ReportTypeTF)

ggplot(data = ReportDF, aes(ReportType, ReportTypeTF)) + 
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Types of Weight Log Methods", x = "Weight Log Methods", y = "Number of Records")
```
\
**Notes:** Earlier when looking at summary statistics for the Weight Log dataset, I decided it may be beneficial to see how dedicated FitBit users are when it comes to logging their weight. Although there are only 8 participants in the Weight Log dataset, over half of the reports are manual, 61.2 percent to be exact. This may mean that users need more encouragement to report their weight, as they may not feel comfortable in doing so. \
\

#### Calculating and plotting daily activity and sleep Statistics for each day of the week\

```{r fig.show="hold", message=FALSE, out.width="50%"}
# Average Active Minutes per day of week 
# Make sure we exclude zeros when calculating mean
DailyActivity2$TotalActiveMinutes[DailyActivity2$TotalActiveMinutes == 0] <- NA
# Split up the data frame for total active minutes by day
SplitMins <- split(DailyActivity2$TotalActiveMinutes, DailyActivity2$DayOfWeek)
# Find the average amount of active minutes for each day and round values
AvgMins <- sapply(SplitMins, mean, na.rm = TRUE)
AvgMins <- round(AvgMins, digits = 2)
# Create data frame
Day <- c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat")
MinsDF <- data.frame(as.factor(Day), AvgMins)
# Plot
ggplot(data = MinsDF, aes(x = fct_inorder(Day), y = AvgMins)) + 
  geom_bar(position= "dodge", stat = "identity", fill = "steelblue") +
  labs(title = "Average Active Minutes per Day of the Week", x = "Day of the Week", y = "Active Minutes") +
  geom_text(aes(label=AvgMins), vjust=1.6, color="white", size=3.5)

# Average Steps per day of week 
DailyActivity2$TotalSteps[DailyActivity2$TotalSteps == 0] <- NA
SplitSteps <- split(DailyActivity2$TotalSteps, DailyActivity2$DayOfWeek)
AvgSteps <- sapply(SplitSteps, mean, na.rm = TRUE)
AvgSteps <- round(AvgSteps, digits = 2)
StepsDF <- data.frame(Day, AvgSteps)
ggplot(data = StepsDF, aes(x = fct_inorder(Day), y = AvgSteps)) + 
  geom_bar(position= "dodge", stat = "identity", fill = "steelblue") +
  labs(title = "Average Steps per Day of the Week", x = "Day of the Week", y = "Steps") +
  geom_text(aes(label=AvgSteps), vjust=1.6, color="white", size=3)

# Average Burned Calories per day of week 
DailyActivity2$Calories[DailyActivity2$Calories == 0] <- NA
SplitCals <- split(DailyActivity2$Calories, DailyActivity2$DayOfWeek)
AvgCals <- sapply(SplitCals, mean, na.rm = TRUE)
AvgCals <- round(AvgCals, digits = 2)
CalsDF <- data.frame(Day, AvgCals)
ggplot(data = CalsDF, aes(x = fct_inorder(Day), y = AvgCals)) + 
  geom_bar(position= "dodge", stat = "identity", fill = "steelblue") +
  labs(title = "Average Burned Calories per Day of the Week", x = "Day of the Week", y = "Calories") +
  geom_text(aes(label=AvgCals), vjust=1.6, color="white", size=3)

# Average Hours of Sleep per Day of the Week
SleepDay2$TotalMinutesAsleep[SleepDay2$TotalMinutesAsleep == 0] <- NA
SplitSleep <- split(SleepDay2$TotalMinutesAsleep, SleepDay2$DayOfWeek)
AvgSleep <- sapply(SplitSleep, mean, na.rm = TRUE)
AvgSleepHours <- round(AvgSleep/60, digits = 2)
SleepDF <- data.frame(Day, AvgSleepHours)
ggplot(data = SleepDF, aes(x = fct_inorder(Day), y = AvgSleepHours)) + 
  geom_bar(position= "dodge", stat = "identity", fill = "steelblue") +
  labs(title = "Average Hours of Sleep per Day of the Week", x = "Day of the Week", y = "Hours of Sleep") +
  geom_text(aes(label=AvgSleepHours), vjust=1.6, color="white", size=3.5)
```
\
**Notes:** The visuals above show averages for some of the daily activities for each day of the week. As we can see, the two days with the most amount of physical activity, on average, were Tuesdays and Saturdays. These two days have the highest average for active minutes, total steps, and calories burned. Interestingly, we can see that it is typical for both the highest and lowest averages to occur during the weekend. Taking a look at the total steps visual, the average daily steps was under the recommended amount of 10,000 for every day of the week. However, as previously discussed, this number could be lowered to 7,500 which would then mean that the average daily steps for every day reached that goal. We can also see that overall, the average amount of calories burned for each day of the week does not vary much. 
Finally, the recommended hours of sleep per night is 7 hours or more according to the CDC. According to the sleep visual, on average, participants reached that amount or are just shy of 7 hours.
\

### Step 6: Act
#### Conclusions:
* If the goal for users is to burn calories, they are more likely to do so by participating in very rigorous to fairly rigorous activities. They could also burn more calories by increasing their daily step count.
* As far as a goal for the number of steps per day, it is very typical for that amount to be 10,000 steps. I believe it would be more beneficial to lower this number to 7,500 to be more realistic and to not overwhelm users. This is because taking 7,500 steps per day, generally has the same overall health effect as 10,000 steps, just fewer calories burned. 
* When it comes to the sleep data, on average, users reached 7 hours of sleep or were just shy of 7 hours. However, not all participants logged their sleep data, most likely due to not wearing the product to sleep. 
* We were able to see that more of the participants log their calories, while fewer users log their sleep data, and only a small amount of users are logging their weight. It is likely that users find wearing a watch at night uncomfortable as well as not feeling comfortable logging their weight. 
 

#### Recommendations for Bellabeat:
* I think it is very important for users to clarify what exactly it is that their goals are. If it is just to simply be more active, and not to lose weight, notifying users to get up and walk around a bit more could be helpful. On the other hand, if the goal of the user is to lose weight, it would be beneficial to notify users to stay on track and to burn the necessary calories to meet their goal.
* I believe it is important for Bellabeat to let their users know that the more data they share, the more likely they will be able to set their own goals and reach them! 
* When it comes to sleep health, notifying users if they have spent an hour in bed awake is important. Encouraging them to move to another location, rather than their bed, will help to prevent insomnia.
* Recommending users to get at least 7 hours of sleep is also important for one’s sleep health. If users are getting less than the recommended 7 hours, encouraging them to try to get more sleep or going to bed at an earlier time could be beneficial.
* Overall, in order to get more data on users’ sleep activity, I believe it is essential to make sure Bellabeat's Time is comfortable to wear while sleeping.
* Promoting body positivity, may help users to feel more comfortable inputting their weight more often. By empowering Bellabeat users, they could feel more safe inputting data about their weight into a database. 
* Overall, making the Bellabeat app more interactive than other typical fitness apps could be a great way to encourage user activity. Allowing them to add friends and share fun workouts could be a great way in doing so! 